\documentclass[twoside]{article}
\usepackage[a4paper, margin=1in]{geometry}

\usepackage{fontawesome5}
\usepackage{hyperref}
\pagenumbering{gobble}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\input{source/commands}

\begin{document}
\fontfamily{lmss}\selectfont
\begin{center}
    \noindent\huge\textbf{Matthew Hammond}
\end{center}\hr
\info{mailto:matthew.hammond.2036@outlook.com}{\faEnvelope}{matthew.hammond.2036@outlook.com}
\hfill
\info{https://github.com/FrozenDude101}{FrozenDude101}{\faGithub}\\
\info{tel:+447858021900}{\faPhone}{+44 7858 021900}
\hfill
\info{https://www.mammond.com}{mammond.com}{\faGlobe}\hr
As an upcoming Computer Science graduate with a predicted First, I have shown my ability to complete work to an excellent standard, and to successfully manage multiple large projects simultaneously while leading the Computer Science Society. In addition, my proactive approach to tackling challenges and my strong communication skills allow me to effectively collaborate within teams. I am excited to apply my knowledge and drive for excellence to a role where I can make meaningful contributions and continue to grow professionally.
\subheading{Education}
\subsubheading{University of Birmingham}{2020--present}
- M.Eng. Computer Science and Software Engineering.\\
- Predicted a First.\vspace{2pt}\\
\subsubheading{Sleaford Joint Sixth Form}{2018--2020}
- A* Maths, A* Further Maths, A Physics, A Computer Science.\vspace{2pt}\\
\subsubheading{Carre's Grammar School}{2016--2018}
- 11 GCSE's including English and Maths.

\subheading{Volunteering}
\subsubheading{Computer Science Society President}{November 2023--present}
- Lead a committee of 14 members to manage a student society with upwards of 400 members.\\
- Ensured events for our members were planned and ran safely, and successfully.\\
- Planned and ran events consisting of upwards of 150 attendees safely and efficiently.\\
\subsubheading{Computer Science Society Postgraduate Research Rep}{December 2022-November 2023}
- Engaged with the Postgraduate Research students within the School of Computer Science.\\
- Improved PGR attendance at events tenfold.

\subheading{Projects}
\subsublinkheading{https://github.com/FrozenDude101/masters-project}{Haskell Visualiser}{JavaScript, September 2023--April 2024}
- Implementing a visualiser for the Haskell programming language for my Final Year Project.\\
- Communicating with users to produce an easy to use web application.\\
- Fitting to existing specifications for easier user adoption.\\
\subsublinkheading{https://github.com/FrozenDude101/DV-SaveManager}{Derail Valley Save Manager}{C\#, July 2022}
- Interfacing with a large pre-existing code base.\\
- Adding and integrating new functionality to a program.\\
- Superseded by game updates.

\subheading{Skills}
\subsubheading{Teamwork and Communication}{}
- Participating in numerous group projects at University, as well as within the Computer Science Society, has led me to learn excellent teamwork and communication skills.\\
- Together we worked well as a team, and completed our assignments to a high standard.\\
\subsubheading{Leadership}{}
- Leading the Computer Science Society, one of the University of Birmingham's largest student societies, has come with a variety of challenges and hurdles to overcome.\\
- I have been able to effectively lead the committee of 14 people to run many events throughout the year.\\
\subsubheading{Time Management}{}
- Managing University, the Computer Science Society, and my Final Year Project has required good time management skills.\\
- I have effectively managed my team to complete my work, actions, and project effectively and to high standards.\vspace{2pt}
\end{document}